Logarithmic Space Verifiers on NP-complete

### 2019-11-15 doc/manuscript.tex
Finally updated content proof

\begin{theorem}
\label{partially}
$|1LNL|_{c} > |1L|_{c}$ where $|\ldots|_{c}$ denotes the cardinality.
\end{theorem}

\begin{proof}
On the one hand, if we suppose that $|1NL|_{c} \neq |1L|_{c}$, then we obtain directly that $|1LNL|_{c} > |1L|_{c}$ since $1L \varsubsetneq 1NL$ and $1LNL$ contains $1NL$, because the prefix $y$ of the instance $x = yz$ could be the empty string. On the other hand, if we suppose that $|1NL|_{c} = |1L|_{c}$, then we can make a bijective relation between a language $L' \in 1L$ and a language $L'' \in 1NL$. Hence, we can create the languages $L''' \in 1LNL$ such that
\[L''' =\{yz: y \in L' \textit{ and } z \in L''\}\]
where  $L' \in 1L$ and $L'' \in 1NL$ are the languages that are linked in our bijective relation. In this way, we can create a bijective relation between these languages $L''' \in 1LNL$ and the corresponding language $L' \in 1L$. However, the set $S$ of all these languages $L''' \in 1LNL$ is a proper subset of $1LNL$, because there are languages in $1LNL$ such that they are not in $S$. Nevertheless, we have that $|S|_{c} = |1L|_{c}$ since there is a bijective relation between these two sets, but we know that $S \varsubsetneq 1LNL$ and thus, $|1LNL|_{c} > |1L|_{c}$.
\end{proof}

@@

As result, $L = NL$ if and only if $2L = 2NL$. We define the class $LNL$ as the languages
\[L''' =\{yz: y \in L' \textit{ and } z \in L'' \textit{ such that } L' \in L \textit{ and } L'' \in NL\}.\]
Therefore, we can deterministic logarithmic space reduce every language $L''' \in LNL$ to a language $L_{1} \in 1LNL$ or to a language $L_{2} \in 1L$ when $L = NL$. In this way, we can make a relation between every language $L_{1} \in 1LNL$ to a language $L_{2} \in 1L$. We can slightly modify this relation to create a new bijective relation just enumerating the languages $L_{i} \in 1LNL$ with a unique and natural number $i$ such that the relation is now with the corresponding language $L_{2, i}$ where
\[L_{2, i} = \{i \sqcup j: j \in L_{2}\}\]
and $\sqcup$ is the blank symbol \cite{Pap03}. We can make this because $1LNL$ is enumerable due to $P$ is also enumerable and $1LNL \subseteq P$ \cite{Pap03}. However, we know for every natural number $i$ that $L_{2, i}$ belongs to $1L$, since $L_{2} \in 1L$ and we can check in a deterministic one-way computation the nonempty prefix substring $i$ without using any amount of space in the work tapes. Hence, we obtain that $|1LNL|_{c} < |1L|_{c}$ using this modified relation which is bijective, because there are languages in $1L$ such that the instances do not contain the blank symbol. However, this is not possible according to the Theorem \ref{partially}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}

>>>>

\begin{theorem}
\label{partially}
$|1NL|_{c} > |1L|_{c}$ where $|\ldots|_{c}$ denotes the cardinality.
\end{theorem}

\begin{proof}
On the one hand, if we suppose that $|1NL|_{c} \neq |1L|_{c}$, then we obtain directly that $|1NL|_{c} > |1L|_{c}$ because of $1L \varsubsetneq 1NL$ \cite{HM81}. On the other hand, if we suppose that $|1NL|_{c} = |1L|_{c}$, then we can make a bijective relation between a language $L' \in 1L$ and a language $L'' \in 1NL$. Hence, we can create the languages $L''' \in 1LNL$ such that
\[L''' =\{yz: y \in L' \textit{ and } z \in L''\}\]
where  $L' \in 1L$ and $L'' \in 1NL$ are the languages that are linked in our bijective relation. In this way, we can create a bijective relation between these languages $L''' \in 1LNL$ and the corresponding language $L' \in 1L$. However, the set $S$ of all these languages $L''' \in 1LNL$ is a proper subset of $1LNL$, because there are languages in $1LNL$ such that they are not in $S$. Nevertheless, we have that $|S|_{c} = |1L|_{c}$ since there is a bijective relation between these two sets, but we know that $S \varsubsetneq 1LNL$ and thus, $|1LNL|_{c} > |1L|_{c}$.

In addition, we obtain that $1NL \subseteq 1LNL$, because the prefix $y$ of an instance $x = yz$ could be the empty string. Moreover, we have that $1LNL \subseteq 1NL$, because the languages in $1LNL$ are decided by nondeterministic one-way logarithmic space Turing machines. In this way, the complexity class $1LNL$ is equal to $1NL$ and thus, we obtain the contradiction that $|1NL|_{c} > |1L|_{c}$ and $|1NL|_{c} = |1L|_{c}$ at the same time. Consequently, the statement $|1NL|_{c} > |1L|_{c}$ must be true by the reductio ad absurdum logic rule \cite{FE16}.
\end{proof}

@@

As result, $L = NL$ if and only if $2L = 2NL$. Therefore, we can deterministic logarithmic space reduce every language $L_{1} \in 1NL$ to a language $L_{2} \in 1L$ when $L = NL$. In this way, we can make a relation between every language $L_{1} \in 1NL$ to a language $L_{2} \in 1L$. We can slightly modify this relation to create a new bijective relation just enumerating the languages $L_{i} \in 1NL$ with a unique and natural number $i$ such that the relation is now with the corresponding language $L_{2, i}$ where
\[L_{2, i} = \{i \sqcup j: j \in L_{2}\}\]
and $\sqcup$ is the blank symbol \cite{Pap03}. We can make this because $1NL$ is enumerable due to $P$ is also enumerable and $1NL \subseteq P$ \cite{Pap03}. However, we know for every natural number $i$ that $L_{2, i}$ belongs to $1L$, since $L_{2} \in 1L$ and we can check in a deterministic one-way computation the nonempty prefix substring $i$ without using any amount of space in the work tapes. Hence, we obtain that $|1NL|_{c} < |1L|_{c}$ using this modified relation which is bijective, because there are languages in $1L$ such that the instances do not contain the blank symbol. However, this is not possible according to the Theorem \ref{partially}. Consequently, we prove the complexity class $L$ is not equal to $NL$.
\end{proof}
